Disparities in Climate-Induced Health Outcomes in the Greater Toronto Area.

### 2022-06-21 outputs/paper/paper.qmd
Updates to paper.qmd and cleaning population data

@@

@@

>>>>

As climate change worsens, the danger it presents to human health worsens as well. The health impacts from climate change are already being demonstrated in parts of Canada. Canada is warming at almost twice the global rate and if this continues, emissions will exceed 2 degrees celcius worldwide.

@@

Temperature data was collected from ...

Pollution data was collected from ...

@@

Tempreature variables of interest: Station Name, Date, Maximum temperature, Minimum temperature, Mean temperature.

Pollution varibales of interest: Pollutant, Month, Year, Average, StdDeviation
